\documentclass{article}
\setlength{\topmargin}{-.25in}
%\setlength{\textheight}{9in}
\setlength{\evensidemargin}{-.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{6.5in}

\begin{document}

\title{Math 160/263 Minitab Assignment \# 1 - Windows Version} 
\author{Chapter 0 - Introduction to Minitab}
\date{Worksheet Name - data1.MTW}
\maketitle

\noindent
{\em  The purpose of this assignment is to familiarize you with the 
statistical software package, Minitab.  You will learn how to enter, edit, 
and view data as well as open and save files.}

\begin{enumerate}

\item  To start Minitab, click on Start \boldmath $>$ \unboldmath Programs 
\boldmath $>$ \unboldmath Minitab 13 for Windows \boldmath $>$ \unboldmath 
Minitab.

\item  Use the {\bf File \boldmath $>$ \unboldmath Open Worksheet} menu 
command to load the worksheet containing the data for this assignment.

\item  The data for the textbook used in Math 160 was omitted from 
the worksheet.  Append columns 1 through 3 with the data given below.

\begin{center}
\begin{tabular}{cll}

Textbook                              & Author & Price \\
\hline
The Basic Practice of Statistics, 2/E & Moore  & 77.75

\end{tabular}
\end{center}

In order to conduct a thorough analysis of the prices of these books, it 
would be desirable to know the length of each book.  This information 
is given below.

\begin{center}
\begin{tabular}{lc}

\multicolumn{1}{c}{Textbook}                       & Pages \\
\hline
A Brief Introduction to Probability and Statistics & 640 \\
Elementary Statistics, 5/E                         & 864 \\
Elementary Statistics, 8/E                         & 800 \\
Elementary Statistics: Picturing the World, 2/E    & 704 \\
Exploring Statistics, 2/E                          & 940 \\
First Course in Statistics, A, 8/E                 & 576 \\
Introduction to Statistics                         & 752 \\
Introduction to the Practice of Statistics, 3/E    & 828 \\
Introductory Statistics, 4/E                       & 880 \\
Introductory Statistics, 6/E                       & 984 \\
Learning Statistics with Real Data                 & 300 \\
Mind on Statistics                                 & 592 \\
Statistics, 9/E                                    & 880 \\
The Basic Practice of Statistics, 2/E              & 619

\end{tabular}
\end{center}


\item  Assign the name 'Pages' to column 4, and enter the number of pages 
for each book.

\item  Now suppose that you would like to compute the price per page.
Use the {\bf Help \boldmath $>$ \unboldmath Search Help ...} menu
command to obtain instructions for the use of the {\bf Calculator}, then
use the {\bf Calc \boldmath $>$ \unboldmath Calculator} 
menu command to do the desired computation.  (Store the 
results in column 5.)

\item  After noticing that {\em Learning Statistics With Real Data} is 
the only paperback in the list, you decide to remove that book from the 
data set.

\begin{enumerate}

\item  Since it is always wise to leave the original data set intact, use the 
{\bf Manip \boldmath $>$ \unboldmath Copy Columns} menu command to copy 
columns 1 through 5 to columns 6 through 10. 

\item  Now use the {\bf Manip \boldmath $>$ \unboldmath Delete Rows} menu 
command to remove row 11 from columns 6 through 10.

\end{enumerate}

\item  You are now ready to save your work and exit Minitab.

\begin{enumerate}

\item  First use the {\bf File \boldmath $>$ \unboldmath Save Project} menu 
command to save your work.

\item  After saving your project, it is safe to exit Minitab.  This can be 
accomplished by using the {\bf File \boldmath $>$ \unboldmath Exit} menu 
command.  

\end{enumerate}

\item  Suppose that you forgot to answer a portion of your assignment.  The 
following exercises will lead you through the process of restarting Minitab 
and opening your project.

\begin{enumerate}

\item  Start Minitab, and use the {\bf File \boldmath $>$ \unboldmath 
Open Project} menu command to open your project.  At this point you could 
continue to work on the assignment.

\item  Since you haven't made any changes, it is not necessary to save 
your work again.  Simply use the 
{\bf File \boldmath $>$ \unboldmath Exit} menu command to exit Minitab.

\end{enumerate}


\end{enumerate}

\end{document}
