\documentclass{article}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{12in}
\setlength{\evensidemargin}{-.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{6.5in}

\begin{document}
\title{Math 160/263 Minitab Assignment \# 5 - Unix Version} 
\author{Chapters 2 and 4 - Probability}
\date{Worksheet Name - data5.MTW}
\maketitle


\noindent
Upper Wabash Tech has two professional schools, business and law.  A 
three-way table of applicants to these professional schools, categorized 
by gender, school, and admission decision is given below.

\begin{center}
\begin{tabular}{lcc|lcc}
\hline
\multicolumn{3}{c}{Business}   & \multicolumn{3}{c}{Law} \\
\hline
       & Admit & Deny &        & Admit & Deny \\
\hline
Male   & 480   & 120  & Male   & \ 10  & \ 90 \\
Female & 180   & \ 20 & Female & 100   & 200  \\
\hline
\end{tabular}
\end{center} 


\begin{enumerate}

\item  Use the {\bf TALLy} command with the {\bf ALL} subcommand to produce  
tables for gender, decision, and school.

\begin{enumerate}

\item  What is the probability that a randomly selected applicant to Upper 
Wabash Tech is male?  female?  

\item  What is the probability that a randomly selected applicant to Upper 
Wabash Tech is admitted?  denied?

\item  What is the probability that a randomly selected applicant to Upper 
Wabash Tech applied to the Business School?  the Law School?

\end{enumerate}


\item  Use the {\bf TABLes} command with the {\bf ROWPercents} subcommand 
to produce a two-way table of gender by decision.

\begin{enumerate}

\item  What is the probability that a randomly selected male applicant is 
admitted?

\item  What is the probability that a randomly selected female applicant is 
admitted?

\end{enumerate}


\item  Use the {\bf TABLes} command with the {\bf ROWPercents} subcommand 
to produce separate two-way tables of gender by decision for each of 
the professional schools.

\begin{enumerate}

\item  What is the probability that a randomly selected male applicant to 
the Business School is admitted?  What is the probability that a randomly 
selected female applicant to the Business School is admitted?

\item  What is the probability that a randomly selected male applicant to 
the Law School is admitted?  What is the probability that a randoly selected 
female applicant to the Law school is admitted?

\end{enumerate}

\end{enumerate}
\end{document}

