\documentclass{article}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\evensidemargin}{-.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{6.5in}

\begin{document}
\title{Math 160/263 Minitab Assignment \# 8 - Windows Version} 
\author{Chapter 4 - Sampling Distributions}
\date{}
\maketitle

\begin {enumerate}

\item  A snack-food company uses a machine to package bags of pretzels.
The bags are supposed to contain 454 grams (g).  In fact, the contents
vary according to a normal distribution with mean $\mu=454$ g and standard
deviation $7.5$ g.

\begin{enumerate}

\item  Use the {\bf Calc $>$ Probability Distributions $>$ Normal} menu 
command to find the probability that an individual bag contains less than 
445 g.

\item  Use the {\bf Calc $>$ Calculator} menu command to find the mean and 
standard deviation for the contents of the bags in a carton of eight.  Use 
the {\bf Calc $>$ Probability Distributions $>$ Normal} menu command
to find the probability that the mean contents of the bags in a carton of
eight is less than 445 g.

\end{enumerate}


\item  A survey by the National Fisheries Institute showed that 25\% of
adults comsume seafood two or three times a week.
If 100 adults are selected at random, then the count of respondents
that consume seafood two or three times a week
has a binomial distribution with parameters $n=100$ and $p=0.25$.

\begin{enumerate}

\item  Use the {\bf Calc $>$ Random Data $>$ Normal} menu command to 
simulate 100 observations of this random variable in each of 40 
columns of the worksheet.

\item  Use the {\bf Calc $>$ Row Statistics} menu 
command to compute the row means for the first 10 columns, the first 
20 columns, and all 40 columns. 

\item  Create graphical and numerical descriptions of the results in
columns 1, 41, 42, and 43.

\item  Briefly describe how the shapes of the distributions compare
with one another, how the means compare with one another, and
how the standard deviations compare with one another.

\end{enumerate}


\end{enumerate}


\end{document}

