\documentclass{article}
\begin{document}

%\title{MATHEMATICS 160}\author{Fall 2002}\date{}
%\maketitle
\begin{center}
\Large Course Information for\\
Basic Statistics\\
Math 160, Section 3\\
Fall 2002
\end{center}

{\bf Overview.}  Statistics is the field of study involving (1) the 
collection, summarization, and analysis of data; and (2) the drawing of 
inferences about a population from the examination of a sample of the 
population.  The goal of this course is to introduce each student to  
the practice of statistics.

\medskip

\begin{tabular}{ll}
\hspace{-.1in}{\bf Contact Information:} 
& Instructor: Professor Douglas Ulmer                \\
& Office: Math 716     \\
& Phone: 621-6861                  \\
& E-mail: ulmer@math.arizona.edu  \\
& Home Page: swc.math.arizona.edu/\verb=~=ulmer/ 
\end{tabular}

\medskip

{\bf Class Meetings.}  The class meets each Monday, Wednesday, and Friday
from 2:00 to 2:50  in PAS 304.

\medskip

{\bf Class Attendance.}  Attendance is expected and is, obviously,
in a student's best interest.  Students are responsible for
all information provided in class and on the course web page.  Class roll
will be taken periodically, and any student who misses the first day
or more than two days may be administratively dropped from the course.
Electronic devices such as cell phones, pagers, watch alarms, etc. must be turned off
during class.

\medskip

{\bf Textbooks.}  The required textbooks is {\em The Basic Practice of 
Statistics}, 2nd Edition, by David S. Moore.

\medskip

{\bf Calculators.}  Each student is required to have, and to know how to 
use, a graphing calculator that can do the statistical calculations correlation 
and linear regression.  (Almost any graphing calculator from TI, HP, or Casio will do.  If in doubt, ask me.)  Some examination questions will require the use of 
such calculators.  In class, I will use a TI-89.

\medskip

{\bf Computer Accounts.}  Each student is also required to have an account
on the Menu/Shell computer system (u.arizona.edu) through which MINITAB, a statistical
software package,  may be accessed.  

Separate instructions on how to set up an account can be found on the course web page.
To access the account, connect to shell.u.arizona.edu using SSH - Secure
Shell software.  To use MINITAB, type {\tt minitab} after the system
prompt. 

Each student is also required to be able to receive e-mail.  This can be done through the u.arizona.edu system. As required by the University of Arizona's Official Student Email
Policy, students are expected to read their email on a frequent and
consistent basis.

\pagebreak

{\bf Homework.}  Exercises from the textbook will be assigned and
collected on a regular basis, and selected exercises from
each assignment will be graded.  Solutions must be neatly written with
each exercise clearly labeled in the left margin.  The student's name, 
course number, and section number must be given at the top of the first 
page, and assignments consisting of multiple pages must be stapled.
No credit will be given for assignments that contain only answers with
no supporting work.  LATE ASSIGNMENTS WILL NOT BE ACCEPTED.

\bigskip

{\bf Minitab Homework.}  Minitab assignments will be provided by the instructor and 
collected on a regular basis.  Solutions must be computer-generated
with each exercise clearly labeled.  The student's name,
course number, and section number must be given at the top of the first
page, and assignments consisting of multiple pages must be stapled.  No
credit will be given for assignments that contain only answers with no
supporting work.  LATE ASSIGNMENTS WILL NOT BE ACCEPTED.

\bigskip

{\bf Examinations.}  Three midterm examinations will be given during the 
weeks indicated in the {\em Course Schedule}, and a final examination 
will be given on {\bf Wednesday, December 18 2:00 pm to 4:00 pm in PAS 304}.  Exams will not be given at any other time and there will be no ``make-up exams.''  If a student 
misses one midterm examination AND if the absence is due to a bona fide 
and documented emergency, then the student will receive a replacement 
score based upon the corresponding part of the final examination.  A 
second missed midterm examination, or a missed final examination, will 
result in a score of zero for that work.  THERE WILL BE NO EXCEPTIONS TO THIS POLICY.

\bigskip

{\bf Office Hours.}  To start, office hours will be held on Wednesdays 1-2 and Thursdays
from 2-4 pm, or by appointment.  When the tutoring room reopens (see below), the Thursday 2-3 office hour will be held there.  These times may change, so check the course home page or call to be sure.

\bigskip

{\bf Other Help.}  The mathematics department provides free tutoring for all lower level courses, on a drop in basis.  This semester, tutoring will start sometime after Labor Day and will be held M-Th 10-3 and Friday 10-2 in the new ``Math East" building (formerly the Stores warehouse).  Details will be announced in class.

\pagebreak

{\bf Course Grades.}  Midterm examinations will be worth 100 points each,
and the final examination will be worth 200 points.  Homework assignments
will be worth 10 points each, but only the ten highest scores will be used
in the computation of the course grade.  Minitab assignments will be
worth ten points each, but only the ten highest scores will be used in the
computation of the course grade.  At the end of the semester, grades will 
be assigned based on the scale given below.

\vspace{.1in}

\begin{center}
\begin{tabular}{c|c}
total points & grade \\ 
\hline
      630-700      & A     \\
      560-629      & B     \\
      490-559      & C     \\
      420-489      & D     \\
\ \ \   0-419      & E

\end{tabular}
\end{center}

\bigskip

{\bf Dropping The Course.}  The last day to drop without a signature is
Friday, September 20, and the last day to drop with a grade of ``W''
(if passing) is Friday, October 18.

\bigskip

{\bf Incomplete Grades.}  If a student fails to complete the course due to 
circumstances unforeseen, then he or she may qualify for a grade of I, 
``incomplete'' if {\bf {\em all}} of the conditions are met:

\begin{enumerate}

\item The student has completed all but a small portion of the required 
work.
\item The student has scored at least 50\% on all work completed.
\item The student has a valid reason for not completing the course on 
time.
\item The student agrees to make up the material in a short period of 
time.
\item The student asks for the incomplete before grades are due - 48 hours 
after the final exam.

\end{enumerate}

{\bf Academic Integrity.}  Students are expected to be familiar with and
abide by the University of Arizona's Code of Academic Integrity and
Student Code of Conduct.  These codes will be strictly enforced, and any
student found to be in violation will be appropriately sanctioned.

\pagebreak

The following is a {\bf {\em tentative}} Course Schedule.  The sections 
refer to {\em The Basic Practice of Statistics}, 2nd Edition.

\vspace{.1in}

\begin{center}
\begin{tabular}{c|c|c|l|c}

week & dates       & sections     & \qquad topics             & notes        
\\
\hline 
1    & 8/26-8/30   & 1.1-1.2      & Distributions             &              
\\
2    & 9/02-9/06   & 2.1-2.4      & Relationships             & Labor Day    
\\
     &             &              &                           & (9/2)        
\\
3    & 9/09-9/13   & 2.5          & Categorical Data          & Exam I       
\\
4    & 9/16-9/20   & 3.1-3.2      & Producing Data            &              
\\
5    & 9/23-9/27   & 4.1-4.2,     & Probability               &              
\\
     &             & 5.1, 5.3     &                           &              
\\
6    & 9/30-10/04  &              & Random Variables          &              
\\
7    & 10/07-10/11 & 5.2          & The Binomial Distribution & Exam II      
\\
8    & 10/14-10/18 & 1.3          & The Normal Distribution   &              
\\
9    & 10/21-10/25 & 4.3          & Sampling Distributions    &              
\\
10   & 10/28-11/01 & 6.1          & Estimation                &              
\\
11   & 11/04-11/08 & 6.2-6.3      & Tests of Significance     & Exam III     
\\
12   & 11/11-11/14 & 7.1          & Inference for $\mu$       & Veteran's 
Day\\
     &             &              &                           & (11/11)      
\\
13   & 11/18-11/22 & 7.2          & Comparing Two Means       &              
\\
14   & 11/25-11/29 & 8.1-8.2      & Inference - Proportions   & 
Thanksgiving \\
     &             &              &                           & Recess       
\\
     &             &              &                           & 
(11/28-11/29)\\
15   & 12/02-12/06 & 9.1-9.2      & The Chi-Square Test       &              
\\
16   & 12/09-12/11 &              & Review                    &

\end{tabular}
\end{center}

\end{document}




