\documentclass{article}
\setlength{\topmargin}{-.25in}
\setlength{\textheight}{11in}
\setlength{\evensidemargin}{-.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\textwidth}{7in}

\begin{document}
\title{Mathematics 160/263 \\ Introduction to the {\it U-System}} 
\author{}
\date{}
\maketitle

\section{Obtaining a {\em U-System} Account}

\begin{enumerate}
\item  Open Netscape or Internet Explorer.
\item  Go to http://www.account.arizona.edu.
\item  Click on {\bf Create CCIT computer accounts}.
\item  Enter your UA NetID User Name and Password, then press {\em Enter}.
\item  Select {\bf U-System} and click on {\bf Continue}.  (If U-System is 
listed in red as one of your current accounts, then you may exit the 
Account program.)
\item  Follow the instructions that are provided.
\end{enumerate}


\section{Connecting to the {\em U-System}}

\begin{enumerate}
\item  Open the SSH Secure Shell Client.  (You may download a free copy 
of the software from http://www.u.arizona.edu/ssh.  If you have difficulty 
with the instructions that are provided, then call 621-HELP to speak 
with a consultant.)
\item  Click on {\bf File \boldmath $>$ \unboldmath Connect}.
\item  Enter the Host Name (u.arizona.edu) and your User Name, then press 
{\em Enter}. 
\item  Click on No, enter your Password, and press {\em Enter}. \\
The first time that you log in to your account, you will be given  
four interface options.  You should select Option 3 -- Use a {\bf Shell}
(command-driven) interface for this and all future sessions.
\end{enumerate}


\section{Downloading files from the {\em U-System}}
\begin{enumerate}
\item  Click on {\bf Window \boldmath $>$ \unboldmath New File Transfer}.
\item  Click once on the file that you would like to download, then 
click on {\bf Operation \boldmath $>$ \unboldmath Download}.
\item  Select the folder to which you would like to download the file, 
then press {\em Enter}.
\item  Click on {\bf Window \boldmath $>$ \unboldmath Close} to close the 
file transfer window.
\end{enumerate}

\pagebreak


\section{Disconnecting from the {\em U-System}}

\begin{enumerate}
\item  Type \ {\bf {\tt exit}} \ at the system prompt 
\boldmath ($>$), \unboldmath and press {\em Enter}.
\item  Click on {\bf File \boldmath $>$ \unboldmath Exit} to close the SSH 
Secure Shell Client.
\end{enumerate}


\section{Changing the Login Shell}
If you are presented with a menu interface after connecting to your 
account, then you will need to change your login shell in order to use 
Minitab.
\begin{enumerate}
\item  Select {\bf M} for Menu, and press {\em Enter}.
\item  Select {\bf Misc}, and press {\em Enter}.
\item  Select {\bf Shell}, and press {\em Enter}.
\item  Enter your password at the prompt, and press {\em Enter}.
\item  Press {\em Enter} once and then again.
\item  Enter {\bf q} for quit and {\bf y} for yes.
\end{enumerate}
Wait about five minutes, then log in to your account again.  You should 
now have a Shell-based interface.

\end{document}
